---
title: "Paperboy Monitor"
format:
  dashboard:
    theme:
      - flatly
    nav-buttons:
      - icon: github
        href: https://github.com/your-org/paperboy
        aria-label: Paperboy on GitHub
logo: assets/logo.png   # remove this line if you have no logo
---

```{r}
#| label: setup
#| include: false

library(DBI)
library(RSQLite)
library(dplyr)
library(tidyr)
library(ggplot2)
library(DT)

source("helpers.R")

# ── Paths ──────────────────────────────────────────────────────────────────────
DB_PATH    <- here::here("data", "paperboy_monitor.sqlite")
STATUS_CSV <- here::here("data", "status.csv")

# ── Load data ──────────────────────────────────────────────────────────────────
status_info <- read.csv(STATUS_CSV, stringsAsFactors = FALSE)

init_db(DB_PATH)
results <- get_latest_results(DB_PATH, status_info)
runs    <- get_run_history(DB_PATH)

# ── Summary counts ─────────────────────────────────────────────────────────────
n_total    <- nrow(status_info)
n_ok       <- sum(results$health == "ok",                        na.rm = TRUE)
n_degraded <- sum(results$health == "degraded",                  na.rm = TRUE)
n_broken   <- sum(results$health %in% c("broken", "error"),      na.rm = TRUE)
n_no_rss   <- sum(results$health == "no_rss",                    na.rm = TRUE)

# ── Last run timestamp ─────────────────────────────────────────────────────────
ts       <- results$tested_at[!is.na(results$tested_at)]
last_run <- if (length(ts) == 0) "Never tested" else
  paste("Last run:", format(max(as.POSIXct(ts)), "%Y-%m-%d %H:%M UTC"))

# ── Colour helpers shared across tabs ─────────────────────────────────────────
health_bg  <- c(ok = "#d4edda", degraded = "#fff3cd", broken = "#f8d7da",
                error = "#f8d7da", no_rss = "#e9ecef", untested = "#e9ecef")
health_col <- c(ok = "#155724", degraded = "#856404", broken = "#721c24",
                error = "#721c24", no_rss = "#495057", untested = "#495057")
```

# Overview

## Row {height=20%}

```{r}
#| content: valuebox
#| title: "Total Scrapers"
#| icon: newspaper
#| color: secondary
n_total
```

```{r}
#| content: valuebox
#| title: "OK"
#| icon: check-circle
#| color: success
n_ok
```

```{r}
#| content: valuebox
#| title: "Degraded"
#| icon: exclamation-triangle
#| color: warning
n_degraded
```

```{r}
#| content: valuebox
#| title: "Broken"
#| icon: x-circle
#| color: danger
n_broken
```

```{r}
#| content: valuebox
#| title: "No RSS"
#| icon: rss
#| color: light
n_no_rss
```

## Row {height=80%}

### Scraper Status {.tabset}

```{r}
#| title: "Scraper Status"
#| label: status-table

display <- results |>
  mutate(
    http_pct     = ifelse(
      is.na(n_articles_attempted) | n_articles_attempted == 0, NA_real_,
      round(n_http_success / n_articles_attempted * 100)
    ),
    pct_headline = round(pct_headline * 100),
    pct_datetime = round(pct_datetime * 100),
    pct_author   = round(pct_author   * 100),
    pct_text     = round(pct_text     * 100),
    tested_at    = ifelse(
      is.na(tested_at), "—",
      format(as.POSIXct(tested_at), "%Y-%m-%d %H:%M")
    )
  ) |>
  select(domain, health, http_pct, pct_headline,
         pct_datetime, pct_author, pct_text, tested_at)

datatable(
  display,
  rownames  = FALSE,
  filter    = list(position = "top", clear = FALSE),
  colnames  = c("Domain", "Status", "HTTP %", "Headline %",
                "Datetime %", "Author %", "Text %", "Last Tested"),
  options   = list(
    pageLength = 30,
    order      = list(list(1, "asc")),
    dom        = "lftip",
    initComplete = JS("function() {
      var api = this.api();
      var col = api.column(1);
      var filterCell = $(api.table().header()).find('tr').eq(1).find('th, td').eq(1);
      filterCell.empty();
      var statuses = ['ok', 'degraded', 'broken', 'error', 'no_rss', 'untested'];
      var select = $('<select class=\"form-control form-control-sm\" style=\"width:100%\"><option value=\"\">All</option></select>')
        .appendTo(filterCell)
        .on('change', function() { col.search($(this).val(), true, false).draw(); });
      $.each(statuses, function(i, d) {
        select.append('<option value=\"' + d + '\">' + d + '</option>');
      });
    }")
  ),
  selection = "none"
) |>
  formatStyle(
    "health",
    backgroundColor = styleEqual(names(health_bg),  unname(health_bg)),
    color           = styleEqual(names(health_col), unname(health_col)),
    fontWeight      = "bold"
  ) |>
  formatStyle(
    c("http_pct", "pct_headline", "pct_datetime", "pct_author", "pct_text"),
    backgroundColor = styleInterval(c(49, 79), c("#f8d7da", "#fff3cd", "#d4edda"))
  )
```

::: {.card-footer .text-muted .small}
`r last_run`
:::

# Domain Detail

```{r}
#| label: domain-detail-data

# Pre-compute history for all domains so the tab renders statically.
# Each domain gets its own sub-tab below.
all_domains <- sort(status_info$domain)

domain_histories <- lapply(setNames(all_domains, all_domains), function(d) {
  get_domain_history(DB_PATH, d)
})
```

## {.tabset}

```{r}
#| label: domain-tabs
#| output: asis

for (d in all_domains) {
  h   <- domain_histories[[d]]
  rss <- status_info$rss[status_info$domain == d]

  # ── badge ───────────────────────────────────────────────────────────────────
  if (nrow(h) == 0) {
    badge <- '<span class="badge bg-secondary">UNTESTED</span>'
    last  <- "Never tested"
  } else {
    badge_class <- switch(h$health[1],
      ok       = "bg-success",
      degraded = "bg-warning text-dark",
      broken   = "bg-danger",
      error    = "bg-danger",
      "bg-secondary"
    )
    badge <- sprintf('<span class="badge %s">%s</span>', badge_class, toupper(h$health[1]))
    last  <- format(as.POSIXct(h$tested_at[1]), "%Y-%m-%d %H:%M")
  }

  rss_link <- if (length(rss) == 0 || is.na(rss) || !nzchar(trimws(rss))) {
    "<em class='text-muted'>No RSS feed</em>"
  } else {
    sprintf('<a href="%s" target="_blank" class="small text-break">%s</a>', rss, rss)
  }

  # ── trend plot ──────────────────────────────────────────────────────────────
  trend_plot_code <- if (nrow(h) == 0) {
    "ggplot() + annotate('text', x=0.5, y=0.5, label='No test history yet', size=6, colour='grey60') + theme_void()"
  } else {
    NULL  # plot built inline below
  }

  # ── emit markdown ────────────────────────────────────────────────────────────
  cat(sprintf("\n### %s\n\n", d))
  cat("::: {.grid}\n")
  cat("::: {.g-col-3}\n")
  cat("**Current status**\n\n")
  cat(badge, "\n\n")
  cat(sprintf("**Last tested:** %s\n\n", last))
  cat("**RSS feed:**\n\n")
  cat(rss_link, "\n\n")
  cat(":::\n")
  cat("::: {.g-col-9}\n")

  # trend plot
  if (!is.null(trend_plot_code) || nrow(h) == 0) {
    cat("```{r echo=FALSE}\n")
    cat("ggplot() + annotate('text', x=0.5, y=0.5, label='No test history yet', size=6, colour='grey60') + theme_void()\n")
    cat("```\n\n")
  } else {
    # Build and print the plot object directly
    p <- h |>
      mutate(tested_at = as.POSIXct(tested_at)) |>
      pivot_longer(
        cols      = c(pct_headline, pct_datetime, pct_author, pct_text),
        names_to  = "metric",
        values_to = "value"
      ) |>
      mutate(
        metric = recode(metric,
          pct_headline = "Headline", pct_datetime = "Datetime",
          pct_author   = "Author",   pct_text     = "Text"
        ),
        value = value * 100
      )

    cat("```{r echo=FALSE}\n")
    cat(sprintf("domain_histories[['%s']] |>\n", d))
    cat("  mutate(tested_at = as.POSIXct(tested_at)) |>\n")
    cat("  pivot_longer(cols = c(pct_headline, pct_datetime, pct_author, pct_text),\n")
    cat("               names_to = 'metric', values_to = 'value') |>\n")
    cat("  mutate(metric = recode(metric, pct_headline='Headline', pct_datetime='Datetime',\n")
    cat("                         pct_author='Author', pct_text='Text'), value = value * 100) |>\n")
    cat("  ggplot(aes(x = tested_at, y = value, colour = metric, group = metric)) +\n")
    cat("    geom_hline(yintercept = 50, linetype = 'dashed', colour = 'grey70') +\n")
    cat("    geom_line(linewidth = 1.1) + geom_point(size = 2.5) +\n")
    cat("    scale_y_continuous(limits = c(0, 100), labels = \\(x) paste0(x, '%')) +\n")
    cat("    scale_colour_manual(values = c(Headline='#e74c3c', Datetime='#3498db',\n")
    cat("                                   Author='#2ecc71', Text='#f39c12')) +\n")
    cat("    labs(x = NULL, y = 'Extraction rate', colour = NULL) +\n")
    cat("    theme_minimal(base_size = 13) +\n")
    cat("    theme(legend.position = 'bottom', panel.grid.minor = element_blank())\n")
    cat("```\n\n")
  }

  # history table
  if (nrow(h) > 0) {
    cat("```{r echo=FALSE}\n")
    cat(sprintf("h <- domain_histories[['%s']]\n", d))
    cat("h |>\n")
    cat("  mutate(\n")
    cat("    tested_at    = format(as.POSIXct(tested_at), '%Y-%m-%d %H:%M'),\n")
    cat("    pct_headline = paste0(round(pct_headline * 100, 1), '%'),\n")
    cat("    pct_datetime = paste0(round(pct_datetime * 100, 1), '%'),\n")
    cat("    pct_author   = paste0(round(pct_author   * 100, 1), '%'),\n")
    cat("    pct_text     = paste0(round(pct_text     * 100, 1), '%')\n")
    cat("  ) |>\n")
    cat("  select(tested_at, health, n_articles_attempted, n_http_success,\n")
    cat("         pct_headline, pct_datetime, pct_author, pct_text, error_msg) |>\n")
    cat("  datatable(rownames = FALSE,\n")
    cat("            colnames = c('Tested At','Health','Articles','HTTP OK',\n")
    cat("                         'Headline%','Datetime%','Author%','Text%','Error'),\n")
    cat("            options  = list(pageLength = 10, dom = 'tip'),\n")
    cat("            selection = 'none')\n")
    cat("```\n\n")
  }

  cat(":::\n")
  cat(":::\n\n")
}
```

# Run History

```{r}
#| label: run-history

if (nrow(runs) == 0) {
  cat("_No test runs recorded yet._")
} else {
  runs |>
    mutate(
      started_at   = format(as.POSIXct(started_at),   "%Y-%m-%d %H:%M"),
      completed_at = ifelse(
        is.na(completed_at), "—",
        format(as.POSIXct(completed_at), "%Y-%m-%d %H:%M")
      )
    ) |>
    datatable(
      rownames  = FALSE,
      colnames  = c("Run ID", "Started", "Completed", "Domains Tested", "Status"),
      options   = list(pageLength = 20, dom = "tip"),
      selection = "none"
    )
}
```
